---
---

## Relational Data Extraction

Relational data are tables that establish a relationship between entities from
other tables.

Suppose we have a table with a record for each unique email address in the Enron
emails, then a second table with a record for each pair of addresses that
exchanged a message is relational data.
{:.notes}

```{r}
email <- enron[[2]]
head(content(email))
```

===

This "To:" field is slightly harder to extract, because it may include multiple
recipients.

```{r, handout = 0}
get_to <- function(email) {
  body <- content(email)
  match <- str_detect(body, '^To:')
  if (any(match)) {
    to_start <- which(match)[[1]]
    match <- str_detect(body, '^Subject:')
    to_end <- which(match)[[1]] - 1
    to <- paste(body[to_start:to_end], collapse = '')
    to <- str_extract_all(to, '\\b\\S+@\\S+\\b')
    return(unlist(to))
  } else {
    return(NA)
  }
}
```

```{r}
get_to(email)
```

===

Embed the above lines in a for loop to build an edge list for the network of
e-mail senders and recipients.

```{r, handout = 0}
edges <- lapply(enron, FUN = function(email) {
  from <- meta(email, 'author')
  to <- get_to(email)
  return(cbind(from, to))
})
edges <- do.call(rbind, edges)
edges <- na.omit(edges)
attr(edges, 'na.action') <- NULL
```

```{r}
dim(edges)
```

===

The **network** package provides convenient tools for working with relational data.

```{r network_graph, results='hide', message=FALSE, handout = 0}
library(network)

g <- network(edges)
plot(g)
```

===

Question
: Is a network qualitative or quantitative data?

Answer
: {:.fragment} It certainly doesn't fall into line with traditional statistical
methods, but the variables involved are categorical. Methods for fitting models
on networks (e.g. ERGMs) are an active research area.
