---
---

## Text mining

Extracting measurements of quantitative varialbes from unstructured information is the "field-work" component of research projects that rely on texts for empirical observations.

- Searching strings for patterns
- Cleaning documents of un-informative strings
- Quantifying string occurrences and associations

===

## Isolate the unstructured information

```{r, eval=FALSE, title="{{ site.handouts }}"}
for (idx in seq(docs)) {
  header_last <- str_match(content(docs[[idx]]), '^X-FileName:')
  header_last_idx <- which(!is.na(header_last))
  header_last_idx <- header_last_idx[[1]]
  content(docs[[idx]]) <- content(docs[[idx]])[-(1:header_last_idx)]
}
```

===

## Functions for cleaning strings

```{r, title="{{ site.handouts }}"}
docs <- tm_map(docs, removePunctuation)
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removeWords, c("department", "email"))
docs <- tm_map(docs, stemDocument)
docs <- tm_map(docs, stripWhitespace)
```

===

## Create Bag-Of-Words Matrix

```{r, title="{{ site.handouts }}"}
dtm <- DocumentTermMatrix(docs)
```

```{r}
inspect(dtm[1:5, 1:10])
```

===

```{r, title = "{{ site.handouts }}"}
dense_dtm <- removeSparseTerms(dtm, 1 - 10 / length(docs))
```

```{r}
inspect(dense_dtm[1:5, 1:10])
```

===

```{r, title="{{ site.handouts }}"}
freq <- findFreqTerms(dtm, 360)
```

```{r}
freq
```

===

## Associations

```{r, title="{{ site.handouts }}"}
assoc <- findAssocs(dtm, "houston", 0.5)
```

```{r}
assoc
```

```{r}
cor(as.matrix(dtm[, c("houston", "anderson")]))
```
