---
---

## Extracting relational data

Relational data are tables that establish a relationship between entities from other tables. Suppose we have a table with a record for each unique address in the Enron e-mails, then a second table with a record for each pair of e-mail addresses that exchanged a message is relational data.

```{r}
doc <- docs[[2]]
content(doc)[1:6]
```

===

The "To:" field is slightly harder to extract, because it may include multiple recipients.

```{r, title="{{ site.handouts }}"}
subject <- which(!is.na(str_match(content(doc), '^Subject:')))
to <- paste(content(doc)[4:(subject[1] - 1)], collapse='')
to_list <- str_extract_all(to, '\\b\\S+@\\S+\\b')
```

```{r}
to_list
```

===

Embed the above lines in a for loop to build an edge list for the network of e-mail senders and recipients.

```{r, title="{{ site.handouts }}"}
edgelist <- NULL
for (i in seq(docs)) {
  doc <- docs[[i]]
  from <- meta(doc, 'author')
  subject <- which(!is.na(str_match(content(doc), '^Subject:')))
  to <- paste(content(doc)[4:(subject[1] - 1)], collapse='')
  to_list <- str_extract_all(to, '\\b\\S+@\\S+\\b')
  edges <- t(rbind(from, to_list[[1]]))
  edgelist <- rbind(edgelist, edges)
}
```

```{r}
dim(edgelist)
```

===

The **network** package provides convenient tools for working with relational data.

```{r network_graph, results='hide', message=FALSE, title="{{ site.handouts }}"}
library(network)

g <- network(edgelist)
plot(g)
```

===

Question
: Is a network qualitative or quantitative data?

Answer
: {:.fragment} It certainly doesn't fall into line with traditional statistical methods, but the variables involved are categorical. Methods for fitting models on networks (e.g. ERGMs) are an active research area.

===

## Scraping online

Scraping websites for data that, like the addresses in the Enron e-mails, are already stored as well-defined variables is a similar process. The structured data are in there, you just have to extract it. The **httr** package can assist with downloading web page content into R as a navigable HTML document.